\Large \bf New Static Analysis Techniques to Detect Entropy Failure Vulnerabilities in Modern Software Projects

### 2018-12-14 paper/paper.tex
work

One common misuse of cryptography is the misuse of entropy. Without properly random inputs, many cryptographic schemes
are vulnerable to basic forms of cryptanalysis. Some cryptographic algorithms, such as DSA, can even disclose long-term secrets
such as the signing key when the random per-message input is low entropy, made public, or nonunique. Such frailty implies that
proper entropy use is a necessary requirement for secure systems.

Detecting this class of bug often requires an examination of the source code; 
issues where outputs from cryptographic algorithms are completely deterministic

>>>>

One common misuse of cryptography is the misuse of entropy. Without properly random inputs, many cryptographic schemes
are vulnerable to basic forms of cryptanalysis. Some cryptographic algorithms, such as DSA, can even disclose long-term secrets
such as the signing key when the random per-message input is low entropy, made public, or nonunique. Such frailty implies that
proper entropy use is a necessary requirement for secure systems. These bugs have appeared
in widely-used software projects. We briefly discuss two historical examples.

\subsection{Debian OpenSSL}

\cite{schneier2008}

\subsection{FreeBSD}

\cite{hovav2016}

\subsection{Approaches}

Detecting this class of bug often requires an examination of the source code; 
bugs that lead to completely deterministic outputs
 from cryptographic algorithms can often be caught easily during the manual
 testing of code before it is released. Issues which persist past release
 typically result from low-entropy inputs rather than no-entropy inputs.
 As such, these bugs can be difficult to discover and track down. One solution
 to this problem, manual auditing, does work (historically, a manual
 inspection of source code is how these vulnerabilities are disclosed and fixed).
 However effective, manual audits can be an expensive solution, and altogether 
 infeasible
 for many projects to do often, especially those reliant on community donations and gratis
 developer work. On the other hand, static analysis tools have their own issues:
 due to classic hardness results, static analysis algorithms must rely on heuristic
 methods and often cannot provide the sufficient guarantees to developers, even
 if they admit soundness for all of their results.

 \subsection{Contributions}
